---
title: "p1805_hw1_jc5457"
output: github_document
---

```{r, echo=FALSE, message=FALSE}
library(tidyverse)
library(ggplot2)
```

# Problem 1
## the dataset
Here's the `penguins` dataset:

```{r}
data("penguins", package = "palmerpenguins")
```

* The variables in this dataset include:
`r colnames(penguins)`
`r class(penguins)`

* The dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columes.

* The mean flipper length is `r mean(pull(penguins,flipper_length_mm))`

## the plot
The scatterplot of `flipper_length_mm (y)` vs `bill_length_mm (x)`
Color points using the `species` variable

```{r chunk_scatterplot}
ggplot(penguins, 
       aes(x=bill_length_mm, 
           y=flipper_length_mm,
           color=species)) + geom_point()

ggsave(
  "scatterplot.png",
  plot = last_plot()
)
```

# Problem 2
Create a data frame comprised of:

* a random sample of size 10 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 10
* a factor vector of length 10, with 3 different factor “levels”
```{r}
dataframe = 
  tibble(
    random_sample = rnorm(10),
    logical_vector = random_sample > 0,
    character_vector = character(length=10),
    factor_vector = factor(c("lv1","lv2","lv3",
                             "lv3","lv3","lv3",
                             "lv3","lv3","lv3","lv3"))
  )
```

Pull the mean of each variable:
```{r}
mean(pull(dataframe, random_sample))
mean(pull(dataframe, logical_vector))
mean(pull(dataframe, character_vector))
mean(pull(dataframe, factor_vector))
```

Try to take the mean of each variable in your dataframe:

* The numeric variable `random_sample` and logical vector `logical_vector` work 
* The character vector `character_vector` and factor vector `factor_vector` don't work

Transfer the variables into numeric variables:
```{r, message=FALSE}
mean(pull(dataframe, as.numeric(logical_vector)))
mean(pull(dataframe, as.numeric(character_vector)))
mean(pull(dataframe, as.numeric(factor_vector)))
```


