---
title: "p1805_hw1_jc5457"
output: github_document
---

```{r, echo=FALSE, message=FALSE}
library(tidyverse)
library(ggplot2)
```

# Problem 1
**Loading the penguins dataset**
```{r}
data("penguins", package = "palmerpenguins")
```

**Descriptions of the penguins dataset**

The variable names in this dataset are: 
`r names(penguins)`.

The table below shows the number of each species in the `species` variable

```{r, echo=FALSE}
summary(pull(penguins,species))
```

The table below shows the number of each island type in the `island` variable

```{r, echo=FALSE}
summary(pull(penguins,island))
```

The table below shows the min, 1st quartile, median, mean, 3rd quartile, max value, and number of NA's of the variable `bill_length_mm`

```{r, echo=FALSE}
summary(pull(penguins,bill_length_mm))
```

The table below shows the min, 1st quartile, median, mean, 3rd quartile, max value, and number of NA's of the variable `bill_depth_mm`
```{r, echo=FALSE}
summary(pull(penguins,bill_depth_mm))
```

The table below shows the min, 1st quartile, median, mean, 3rd quartile, max value, and number of NA's of the variable `flipper_length_mm`
```{r, echo=FALSE}
summary(pull(penguins,flipper_length_mm))
```

The table below shows the min, 1st quartile, median, mean, 3rd quartile, max value, and number of NA's of the variable `body_mass_g`
```{r, echo=FALSE}
summary(pull(penguins,body_mass_g))
```

There are `r nrow(penguins)` rows and `r ncol(penguins)` columns.

The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = T)`


**The plot**

The scatterplot of `flipper_length_mm (y)` vs `bill_length_mm (x)`
Color points using the `species` variable

```{r chunk_scatterplot}
ggplot(penguins, 
       aes(x=bill_length_mm, 
           y=flipper_length_mm,
           color=species)) + geom_point()

ggsave(
  "scatterplot.png",
  plot = last_plot()
)
```

# Problem 2
**Create a data frame**
This code chunk creates a data frame comprised of:

* a random sample of size 10 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 10
* a factor vector of length 10, with 3 different factor “levels”
```{r}
dataframe = 
  tibble(
    random_sample = rnorm(10),
    logical_vector = random_sample > 0,
    character_vector = character(length=10),
    factor_vector = factor(c("lv1","lv2","lv3",
                             "lv3","lv3","lv3",
                             "lv3","lv3","lv3","lv3"))
  )
```

**Pull the mean of each variable**
```{r}
mean(pull(dataframe, random_sample))
mean(pull(dataframe, logical_vector))
mean(pull(dataframe, character_vector))
mean(pull(dataframe, factor_vector))
```

Try to take the mean of each variable in your dataframe:

* The numeric variable `random_sample` and logical vector `logical_vector` work 
* The character vector `character_vector` and factor vector `factor_vector` don't work

**Transfer the variables into numeric variables**
```{r, results = 'hide', warning = FALSE}
as.numeric(pull(dataframe, logical_vector))
as.numeric(pull(dataframe, character_vector))
as.numeric(pull(dataframe, factor_vector))
```

Logical and factor vectors are successfully converted to numeric vectors.
Character vector can not be converted to numeric vector.

The failure of taking mean in the above section is because only numeric and logical vectors can take means. For logical vector, 1 represents TRUE and 0 represents FALSE.


